4.1 Eyewear
	4.1.1 Description: The product shall provide eyewear or goggles to operate the device
	4.1.2 Source: Fernando Do Nascimento
	4.1.3 Constraints: The eyewear may not be comfortable for all users to use
	4.1.4 Standards: None
	4.1.5 Priority: 1

4.2 Cables
	4.2.1 Description: The product shall provide all the necessary cables (USB, Power, etc) for the user to operate the Eye Tracker.
	4.2.2 Source: Fernando Do Nascimneto
	4.2.3 Constraints: The lenght of the cables may not meet the needs of the customer and the power cable will only be compatible with U.S. Power Standards (110V~120V).
	4.2.4 Standards: United States Voltage Standards.
	4.2.5 Priority: 2
	
4.3 Camera
	4.3.1 Description: The product shall provide the user with a camera mounted to the eyewear.
	4.3.2 Source: Fernando Do Nascimento
	4.3.3 Constraints: The camera shall only be a MIPI camera module.
	4.3.4 Standards: None.
	4.3.5 Priority: 1
	
4.4 Protective Case
	4.4.1 Description: The product may be enclosed in a case in order to protect the item from water and dust.
	4.4.2 Source: Fernando Do Nascimento
	4.4.3 Constraints: Provide a case that will protect the device, but also provide the ventilation necessary to prevent overheating.
	4.4.4 Standards: IP55
	4.4.5 Priority: 3
	
4.5 Eyewear Safety Cord
	4.5.1 Description: The eyewear may come with a safety cord.
	4.5.2 Source: Fernando Do Nascimento
	4.5.3 Constraints: The safety cord may not be convenient for the customer to use.
	4.5.4 Standards: None.
	4.5.4 Priority: 4
	
4.6 Manuals
	4.6.1 Description: The product shall include all the instruction manuals that properly explains how to operate the Eye Tracker and how to install all the necessary software.
	4.6.2 Source: Fernando Do Nascimento
	4.6.3 Constraints: The customer must have a PDF document reader in order to access the manuals.
	4.6.4 Standards: None.
	4.6.5 Priority: 3

4.7 Software
	4.7.1 Description: The product shall provide the necessary software for the customer to operate the Eye Tracker.
	4.7.2 Source: Fernando Do Nascimento
	4.7.3 Constraints: The software is compatible with Linux OS, MAC OS X, and Windows OS.
	4.7.4 Standards: None.
	4.7.5 Priority: 3
